Title Goes Here

### 2020-02-25 paper/paper.tex
Slight rewording and restructuring

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
% \renewcommand{\shortauthors}{Trovato and Tobin, et al.}

@@

Despite these advantages Haskell provides for creating EDSLs, there are a few
constructs which have often proved illusive to embed in an EDSL. One prominent
example is that of a \ttt{case} expression. Pattern matching is a convenient way
to implement control flow structures and to view components of data structures,
so it is frequently a desirable feature for many EDSLs.

@@

x :: Either Char Int
x = Left 'a'
example :: Int
example =
  internalize (externalize
    (case x of
      Left  c -> ord c
      Right i -> i))

@@

\section{Representing tail recursion}
\begin{tcolorbox}
  \textbf{TODO}: Expand this section
\end{tcolorbox}

@@

The \ttt{Name t} type represents a lambda variable identifier together with its
type \ttt{t}:

@@

(Note that the \ttt{ScopedTypeVariables} extension is enabled.)

>>>>

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
% \renewcommand{\shortauthors}{Trovato and Tobin, et al.}
\renewcommand{\shortauthors}{Young and Gill}

@@

Despite these advantages Haskell provides for creating EDSLs, there are a few
constructs for which representations have proven illusive. One prominent example
is that of a \ttt{case} expression. Pattern matching is a convenient way to
implement control flow structures and to view components of data structures, so
it is frequently a desirable feature for many EDSLs.

@@

x :: Either Char Int
x = Left 'a'

example :: Int
example =
  internalize (externalize
    (case x of
      Left  c -> ord c
      Right i -> i))

@@

\section{Representing tail recursion}
\begin{tcolorbox}
  \textbf{TODO}: Expand the explanation in this section
\end{tcolorbox}

@@

The \ttt{Name t} type represents a lambda variable identifier together with its
type \ttt{t} (Note that the \ttt{ScopedTypeVariables} extension is enabled.):

@@
